 Handheld computing/tracking device:
 	 Smartphones
 	 Tablets
 	 PDA
 	 
 	 
 	 1 Hvad er det?
 	 ----Hvad gør det? (hvilken form for input/output?)
 	 2 Hvorfor bruges den?
 	 ----Hvorfor er den relevant?
 	 ----Hvorfor mangler den relevans?
 	 
Handheld computing/tracking devices such as smartphones, tables and PDA's are all relative small handhelds that the user are able to carry around. Such device all have a screen (some old PDA's will not have) and a Wi-Fi or Bluetooth connection module that allows them to send/receive data. This data can then be projected onto the screen, to inform the user.

%The PDA functions as a personal digital assistant, who will keep track of the user's calender or have a calculator program. Two popular PDA's are the iPod touch and BlackBerrie which are still in use. 
%The Smartphone are much alike the PDA, but have other features such as the ability to receive or make phone calls. Smartphones also a varity of apps that allows 3rd party programs to be installed. Such programs could be digital games or social media programs like Facebook or Twitter. Two popular smartphone series would be the iPhoneor the Samsung galaxy.
%The Tablet is bigger in size compared to the PDA and smartphone, and won't fir in the users pocket. They serve almost the same purpose as the smartphones but have more computing power and memory storage. The tablets are used to satisf the needs that laptop covers that a smartphone will not do competent enough. Such needs could be to surf the world wide net, which many do on their laptop or home PC. This can be done on a smartphone but the screen is often seen as too small. The tablet have a bigger screen and thereofre provides a better experience. Two popular tablet would be the iPad and the Surface. 

These handheld computing/tracking devices can al be used to project a map or in anoter way navigate the user, trough text, symbols or pictures shown on the screen. They can be brought in the most electronic stores and can be carried around in the users pocket(with the exception of the tablet which would need a bag to be hands free). 

These devices needs some basic digital use know-how, in order to be used functionally. In order to use the device to navigate trough a given method, the user would have to start the device and navigate to the right program/app in order to get started. This could potentially lay of some users as it could seems confusing for some of them. The modern devices are also fairly expensive. 