\sinote{Afgræns i afgrænsningen; vi vil kun arbejde med software med øje til handheld devices}

\subsection{Handheld Devices} % (fold)
\label{sub:device}

% subsection subsection_name (end)
 	 
Handheld computing/tracking devices, such as smartphones, tablets and PDA's, are all relatively small and users are able to carry them around. Such devices have a screen, with the exception of some older PDAs, and a Wi-Fi or Bluetooth connection module, that allows them to send and/or receive data. This data can then be projected onto the screen, to inform the user.

%The PDA functions as a personal digital assistant, who will keep track of the user's calender or have a calculator program. Two popular PDA's are the iPod touch and BlackBerrie which are still in use. 
%The Smartphone are much alike the PDA, but have other features such as the ability to receive or make phone calls. Smartphones also a varity of apps that allows 3rd party programs to be installed. Such programs could be digital games or social media programs like Facebook or Twitter. Two popular smartphone series would be the iPhoneor the Samsung galaxy.
%The Tablet is bigger in size compared to the PDA and smartphone, and won't fir in the users pocket. They serve almost the same purpose as the smartphones but have more computing power and memory storage. The tablets are used to satisf the needs that laptop covers that a smartphone will not do competent enough. Such needs could be to surf the world wide net, which many do on their laptop or home PC. This can be done on a smartphone but the screen is often seen as too small. The tablet have a bigger screen and thereofre provides a better experience. Two popular tablet would be the iPad and the Surface. 
Devices like smartphones and tablets are already in use, and they are very popular. This means that for many users, a solution with a downloadable program or application, would be easily adapted. Other navigation programs/applications that they have already used, could have similarities with the solution used in this project, which will ease apdaption even more. These devices are also very portable and can be taken to the hospital without much effort. They can also be used to render a map or otherwise assist the user with navigation, for instance through text, sound or pictures.

For these devices to be used as intended, they requires some prior basic digital knowledge. In order to use the device to navigate trough a given method, the user would have to start the device and navigate to the appropriate application in order to get started. This could potentially hinder some users as this could be confusing to them.

%The modern devices are also fairly expensive which could make them less attractive to users.

\subsection{QR-code} % (fold)


QR-codes are barcode that returns data when scanned. The code is represented by black boxes on a white square grid background. All by how the boxes are located, the code will send different data.

In order to read the data, a scanner have to be used. A camera from a smartphone can be used for this purpose, as long there are a app that supports format. Such apps can be found on nearly all smartphones \cite{QR_smart}. The QR-code can be used to lead users to websites and are used often in different kind of commercial ways\cite{QR_url}.

It easy to read the QR-code if you already have an app installed on your smartphone. It's also easy to make your own codes as Google have released a free tool to generate them\cite{QR_Google}.It's also rather easy to set up a QR-code system in a effective way\cite{QR_easy}.

The relevans for this project is how it will take little time to set up\cite{QR_rel1} and how some people allready knows how use them as they are widely spread\cite{QR_spread}. Even if a code is damaged it will still be usable, even if up to 30\% of the code is missing\cite{QR_dama}. This also means it will be possible to implant images in the code and still have it working\cite{QR_image}.

A reason for not to use the codes could be that some users might exploit the system. If the print their own codes with links certain websites it could be a very unpleasent experience for the other users\cite{QR_urlbad}. In worst case scenarios they could be used to steal personal information\cite{QR_information}.
In order for the codes to be efficient, they also have to placed at many locations at the hospital. The users should always be able to find them when they want to use them. This could leave to frustration if seems to be nowhere to find for the user.

 % 	 1 Hvad er det?
 % 	 ----Hvad gør det? (hvilken form for input/output?)
 % 	 2 Hvorfor bruges den?
 % 	 ----Hvorfor er den relevant?
 % 	 ----Hvorfor mangler den relevans?
 
\subsection{Accelerometer}

The Accelerometer is a transducer that measures acceleration. The acceleration could be static if the device is at hold an only affected by gravity, or dynamic if it moves around\cite{acc_engi}. Accelerometers is used in many different ways and are also used in a lot of different applications, such the PlayStation 3 DualShock 3 remote\cite{acc_ps3} or in a Nokia 5500 sport\cite{acc_nokia}.


The accelerometer is able to detect vibrations, change of magnitude or to direction\cite{acc_engi}. Some accelerometers works by relying on the piezoelectric effect that delivers electronic output from a variety of crystals inside the device\cite{acc_piezo}. This electronic output can then be read by a computer and used to generate information about the state of the accelerometer.


The accelerometer is among other used because it can reliable be applied in car GPS systems. It uses the technique dead reckoning that estimates ones position based on previously coordinates and current vector movement\cite{acc_dead}. The accelerometer has also proven itself useful in some science aspects, such as earthquake investigations or monitoring active volcanoes\cite{acc_vulkan}. 


The accelerometer is relevant for this project, as it can be used to position the users if it's incorporated in a device that is going to be carried along side the current user. In this way it could be used to see if the user is following the generated path or if he/she have moved outside of it. The accelerometers that could be used for this project could be the LIS302DL as it is rather cheap and compact\cite{acc_price}\cite{acc_LIS302DL}. This accelerometer have already been incorporated in the original iPhone\cite{acc_iPhone}.


By using the accelerometer to navigate trough dead reckoning will have a certain intracity to it\cite{acc_inacc}. This could result in false information about were the user currently is which could be problematic when working in multipler floors. As for example, the systems makes a path that uses an elevator. Because of the inaccuracy the systems believes the man is standing just outside the elevator, but he is in fact moving upwards with it. This means that when he gets outside the elevator, on another floor, and starts moving the system will no longer be able to correctly guide him trough the building. 