
\chnote{heading What and Why}
\sinote{Beskriv at google maps virker indendørs}

Google Maps:
google maps, is a service, which takes longitudes and latitudes from for instance a gps, it show yuor position and your taget position on a map, and plots a rute to your target. this is used around the world to navigate you around, but this is commonly used outside, because the gps is not as effective indoor as it is outside.  \chnote{link/source}

what is QR code, QR code is two-dimensonal barcode, it is an machine readable label that is attached to an item and that label records information related to that item. the relevance to our topic is that we can store information in the code about the rooms and the building in the code. 

what is RFID, RFID (Radio Frequency Identification) a radio technology that makes it possible, just like barcodes, to identify different objects. the main different between these two technologies is that the bar code is a line of sight technology and RFID is wireless, as long as it is within visible distance. The readable distance varies depending on the type of RFID tag. The information exchanged can be in many different formats such as text, numbers , audio or video, It depends on the size of RFID the tag built-in memory. 

There are, different RFID tags they can be passive, active or battery-assisted. tags can be read-only "one times read" or read-write "multiply times", have a seial number or can be plank for the owner to write somthing on it. To put into perspective this to our subject, a read-only tag can be used to find an object such. a printer that does not change it's name or property. read-write tag, can be used to track patients, the information can be chance name and CPR number to match the person who wears it.  

http://www.scienceprog.com/how-does-rfid-tag-technology-works/

http://www.enigmatic-consulting.com/Communications_articles/RFID/Link_budgets.html

http://www.rf-id.com/6information/rfid_info_techexplained.htm


