%!TEX root = ../../Master.tex
\subsection{Location Fingerprinting}
In location fingerprinting, there are to main techniques that have been chosen for this project. It is "QR-code" and "RFID".
Location fingerprinting is method of recognizing devices by giving them a electronic fingerprint, such as a unique id.

\paragraph{QR-code} % (fold)
QR-codes are barcodes that returns data when scanned. The code is represented by black boxes on a white square grid background. All by how the boxes are arranged, the code will represent different data.

In order to read the data, a scanner has to be used. A camera from a smartphone can be used for this purpose, as long there are an app that supports this particular format. Such apps can be found on nearly all smartphones\cite{QR_smart}. The QR-code can be used to lead users to websites, and are used often in different kind of commercial ways\cite{QR_url}.

It is easy to read the QR-code if you already have an app installed on your smartphone. It is also easy to make your own codes as Google have released a free tool to generate them\cite{QR_Google}.It is also rather easy to set up a QR-code system in a effective way\cite{QR_easy}.

The relevance for this project is how it will take little to no time to set up\cite{QR_rel1}, and how some people already knows how use them as they are widely spread\cite{QR_spread}. Even if a code is damaged it will still be usable, all up to 30\% of the code can be missing\cite{QR_dama}. This also means it will be possible to implant images in the code and still have it working\cite{QR_image}.

A reason for not to use the codes could be that some users might exploit the system. If they print their own codes with links to certain websites it could be a very unpleasant experience for the other users\cite{QR_urlbad}. In worst case scenarios they could be used to steal personal information\cite{QR_information}.
In order for the codes to be efficient, they also have to placed at many locations at the hospital. The users should always be able to find them when they want to use them. This could leave to frustration if they seems to be nowhere to find for the user.


\paragraph{RFID}
%Hvad er det?
%Output/Input?
%Hvorfor bruges det?
%Hvorofr er det relevant
%Hvorfor er det ikke relevant?

RFID (Radio Frequency Identification) is a radio technology that makes it possible, just like barcodes, to identify different objects. the main difference between these two technologies is that the barcode is a line of sight technology, and RFID is wireless, as long as it is within visible distance. The readable distance varies depending on the type of RFID tag. The information exchanged can be in many different formats such as text, numbers, audio or video. The signal is send with via magnetic fields\cite{RFID_magnetic}.

There are different types of RFID tags each with different purposes. There are the active, semi passive and passive. The active tag can broadcast its radio waves to a RFID reader. The semi passive is different as it has no means of broadcasting on its own and will need the RFID reader to draw power from\cite{RFID_semiActive}. The passive tag does not have its own battery and will therefore need the RFID reader to supply power just like the semi-active tag. The semi-passive tag does however have a battery to supply its circuit with power\cite{RFID_AllTypes}.

The RFID tag is useful because it can help with identifying objects or persons who have a tag implanted\cite{RFID_FAQ}. A RFID reader can automatically find and read the tag if it is located inside the tags range. Wallmart uses RFID to automatically store data when curtain goods arrive, which will save them time and energy\cite{RFiD_inc}. Passive RFID tags have also been developed to be used on cars in order to identify them. It is being considered for cross border control other uses as roll toll collection\cite{RFID_car}. This will make it easier for the driver if he/she can automatically pay tolls. This is used in the Danish Brobizz\cite{RFID_brobizz}   

In this project the tags could be used to position the users as they go trough the building. The active tags could be on the user or device, and when they comes near a reader the reader could tell a server where the tag have been read. In that way the user will be repositioned every time they comes near a "checkpoint". These "checkpoint" could be placed every time there was a turn or a door, as the route then could be planned from that position.

A problem with this solution would be that the users will not be positioned when they are in a middle of a hallway without doors, as no readers will be near them. To get around this problem, the complex should be filled with readers everywhere. The readers will also run low on power at some time, and will need to have it battery replaced. This could evolve into a major project if all the hallways have been plastered.