%!TEX root = ../../Master.tex
\section{Organization} % (fold)
\label{sec:organization}

\sinote{Infrastruktur nødvendig skal beskrives her.}

\sinote{Beskriv hvordan et hospital er som et miljø}

Interference with medical device

Incidents of radio frequency interference between cellular phones, radio broadcasters, wifi devices and medical devices have been reported. Older models of pacemaker, defibrillators and hearing aid devices was being influenced by near encounter of cellular phones causing undesirable effects as not having control of heartbeat etc. The problem was that RF fields were interfering, but standards have made both for medical devices and consumer devices to these does not occur any more. 

http://ewh.ieee.org/soc/embs/comar/interfer.htm

http://www.ce-mag.com/archive/06/ARG/case.htm

\sinote{Skriv ikke om politik i dette område. Beslutningstagen skal flyttes op i interessenter}

In this section we will cover which procedures are needed in order to realize a software solution for our initiating problem (\cref{sub:init}).

In a decision process the following phases will typically happen. \cite{Sjaelland}

%%\begin{description}
%%	\item[Idea and initiative phase] A problem is defined by the citizens, media or political organisation.
%%	\item[Preparing phase] The problem will be reviewed according to the health legislation.
%%	\item[Decision phase] The problem is presented and a committee is established. This committee will typically work with consultants to specify the requirements of the solution.
%%	\item[Implementation phase] The solution will be implemented. 
%%
%%
%%\end{description}
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
	\item \textbf{Idea and initiative phase} A problem is defined by the citizens, media or political organisation.
	\item \textbf{Preparing phase} The problem will be reviewed according to the health legislation.
	\item \textbf{Decision phase} The problem is presented and a committee is established. This committee will typically work with consultants to specify the requirements of the solution.
	\item \textbf{Implementation phase} The solution will be implemented. 
\end{itemize}


Between the decision phase and the implementation phase, the project will be announced as a public supply contract for suppliers to tender. \cite{Union2004}. Suppliers will then submit their solutions. The solution that fits the problem's requirements best, gets the contract. 

% section organization (end)