%!TEX root = ../../Master.tex

\section{Technology} \label{tech}

% \kanote{Der efterfølgende stykke har jeg ikke skrevet. Jeg synes godt vi kan beholde meningen, og så bare skrive det om, så vi indlejrer definitionerne, og ikke referer til andre steder? OGSÅ: ideen om at kort beskrive aspekterne af navigation er godt, men skal det stå her?}
% In order to navigate individuals indoor, it is important to always find the most optimal route based on the users prerequisites. This makes wayfinding technologies very important to our project, and we will cover this in \cref{sub:way}. For any wayfinding technique two parameters is required: a start and an end location. The start location can be determined by positioning the individual. This is done using the methods described in \cref{sub:pos}. Positioning have some requirements that the infrastructure has to comply with, we will define those requirements in \cref{sub:infra}.

Before it is possible to develop an optimal solution to a problem, it is necessary to understand the technology at one's disposal. But since understanding technology is time consuming, it is important to analyse which to focus on. In the following section, technologies have been selected that were predicted to have the most relevance to this problem, and analysed how they could be used in a possible software solution. It is important to note, that there have only been analysed technologies that support a possible solution to the entirety of this project, with a few exception. These exceptions have been included because their hold a prominent role in a common optimal solution to a similar problems.

The analysis of the technologies follows a certain simple method. We describe the different existing digital technology, and analyse their relevance to our initiating problem. We then outline the function of a given technology, and determine its relevance by examining why the technology is in use, and specifically which traits makes the technology relevant for our problem. We subsequently describe any undesirable traits which will decrease the usefulness in a possible solution.

 \label{sub:techmethod}
This method gives a good overview of the usefulness of the given technology, without going into much detail. Details, that are deemed important for understanding a solution or is not otherwise easily obtainable, will be included in a later theoretical chapter.


\input{Chapters/problem_analysis/computing_tracking_devices.tex}

\input{Chapters/problem_analysis/Google_Maps_RFID_QR_code.tex}

\input{Chapters/problem_analysis/GPS.tex}

\input{Chapters/problem_analysis/Location_Fingerprinting.tex}

\input{Chapters/problem_analysis/Accelerometer.tex}

\subsection{Summary}
This section analysed which technologies are considered relevant for a solution. Wi-Fi and accelerometer are regarded as the optimal tools for positioning in this project. As seen in \cref{orgwifi} Wi-Fi is already implemented in most hospitals, reducing implementation costs. Wi-Fi can be used for positioning inside a building, and an accelerometer can be used to reduce Wi-Fi power consumption. Handheld computing/tracking devices are considered the optimal solution for relaying information, due to their versatility.
%\input{Chapters/problem_analysis/positioning.tex}