%!TEX root = ../Master.tex
\chapter{Conclusion}

To conclude, the aim of this report was to analyse the need for and the requirements of an indoor navigation software system, which would allow users to personalize their navigation, in order to offer a better alternative when navigating a large building complex, such as a hospital. It was shown that many pathfinding issues are not being met by current navigation methods, and that certain usergroups are not able to effectively utilize the current systems. In order to combat this, newer technologies with relation to navigation was examined for insight into a way of solving the problems. The demands that needs to be met were defined and due to time constraint, a delimenation was made in order to focus the effort on a core of requirements.

In order to solve the navigation problem, research into graph theory and relevent pathfinding algorithms was conducted. The strengths and weaknesses of different types of graphs and the way of mapping and representing them was described, and the importance of calibrating the graph was discovered. 

Combinding the knowledge of graph theory and indoor navigation issues, certain problems that arose when applying graph theory to fit hospital navigation needed to be adressed. There were problems with how to map the building using graph theory, while preserving information on the different properties of hospital infrastructure. These were solved through a modelling process that while it does not resemble the real building, preserves all the needed information, while storing it in a more compact manner. Another major issue was the matter of algorithm runtime while using traditional algorithms. The solution to this problem was a way of precalculating certain paths before runtime, and this FLAWLESS algorithm became the cornerstone for the entire solution.

The program that was developed in accordance with the results from the report, is able to \kanote{hvad kan vores program egentligt?}

A couple of observations that was made throught the creation of this report follows. The process of calibrating the graph in relation to the actual building, is considered to be paramount in order for the pathfinding algorithm to be able to find the optimal solution without failure. Since the algorithm is to remove all decition making from the user, it should never produce a less than optimal route.