%!TEX root = ../Master.tex
\chapter{Discussion}

\section{Possible program improvements}

Consider the following situation; an user wants to find the fastest route from first floor to third floor. The user does not have any disabilities so both elevators and stairs can be part of the fastest route. The current program would most likely guide the user to the elevator from the first floor to the third floor. However it would be a problem if the elevator was already in use at the sixth floor. The user would then have to wait for the elevator to descent. This could take some time. If the program had the ability to track the location of the elevator, it could use this information in the algorithm of the program. The program would then have enough data to guide the user up the stairs, providing the user with a faster route.
\annote{Er der flere forbedringer eller funktioner som kam kobles på?}
\section{Suggestions for Further Research}

The Flawless algorithm is made to work in complexes. So far hospitals have been the focus of this project, but other complexes should be able to integrate this system as well. Such complexes could be shopping malls, ferries or exhibition halls. 

The shopping mall could benefit from this system as wheelchairs would be able to find elevators with more ease, and customers in general would easier find the various hops they are looking for. Ferries could also benefit from the system as they have travelling businesses men/women who might need to work doing the their travel. Because of the stress that comes with travelling\cite{future_stress} it would make a more pleasant experience if some stress factors like navigating or getting lost could be removed or subdued. The current system would not work as it is at a ferry because of the way it gets the user position. The accelerometer that keeps track of how the user shift direction and moves trough the complex, would be disturbed every time the ship tilted or changed direction. A solution to this would be to solely rely on the Wi-Fi to find the users start position and to keep track of them when they are on the move. Exhibition halls are relevant to look at as s lot of people who have never been in these halls and could need help finding their way to the various booths. If the visitors could use the system to find their way to the booths they are looking for, less people would get lost and here would be less clutters of people as the times used on going from one pace to another will be reduced.