%!TEX root = ../Master.tex
\chapter{Problem Solution}
\label{cha:solution}





\section{Structure} % (fold)
\label{sec:structure}

\begin{description}
	\item[Generate shortest route] 
	Generates most optimal route from A to B based on input. Uses a wayfinding algorithm to calculate the most optimal route through a set of vertices from a graph.

	Input:
	\begin{itemize}
		\item Start vertice by id (or name)
		\item Destination vertice by id (or name)
		\item Graph
	\end{itemize}
	Returns list of vertices the route is going through. The list is ordered starting with the vertex closest to A.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item[Get start position from user] 
	Asks the user for start vertex. Could be vertex id (or name)

	Returns start vertex.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item[Get destination from user] 
	Asks the user for destination vertex. Could be vertex id (or name)

	Returns destination vertex.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item[Parse file for vertices] 
	Parses all the vertices out of a file.

	Input:
	\begin{itemize}
		\item File containing graph data
	\end{itemize}
	Returns all vertices in input file.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item[Parse file for edges] 
	Parses all the edges out of a file.

	Input:
	\begin{itemize}
		\item File containing graph data
	\end{itemize}
	Returns all edges in input file.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item[Calculate distance between 2 vertices] 
	Calculates the distance between 2 vertices using e.g. hamming or euclids distance.

	Input:
	\begin{itemize}
		\item Vertex1
		\item Vertex2
	\end{itemize}
	Returns the distance between 2 vertices.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item[Get adjacent edges] 
	Gets all the edges connected to the specified vertex.

	Input:
	\begin{itemize}
		\item Vertex
	\end{itemize}
	Returns list of found edges.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{description}

\input{Chapters/problem_solution/implementation_graph_theory.tex}

% section structure (end)